Homework_2

### 2022-09-05 hw2/anshit/Homework_2.Rmd
added submisison.Rmd

```{r}
# imports
library(ggplot2)
library(cowplot)
library(reshape2)
# library(factoextra)
```

@@

```{r}
# Calculation of best 'K'
elbow_graph_data <- data.frame(K=integer(), sum_of_square=double())
for(k in seq(1, 10, by=1)){
  km.res <- kmeans(as.matrix(iris_data[,1:4]), k, nstart = 25)
  elbow_graph_data[nrow(elbow_graph_data) + 1, ] = c(k, km.res$tot.withinss)
}
```

@@

```{r}
# renaming predicted clusters according to categorical response variable
renamed_clusters <- c("versicolor", "setosa", "virginica")[best_km$cluster]
```

```{r}
kmeans_basic_table <- data.frame(best_km$size, best_km$centers)
kmeans_basic_df <- data.frame(actual_value=iris_data[,5], prediction=renamed_clusters)
```

```{r}
kmeans_basic_table
```

@@

```{r}
prediction_accuracy <- round(sum(kmeans_basic_df$actual_value == kmeans_basic_df$prediction) / nrow(kmeans_basic_df) * 100, 2)
print(paste('Accuracy Acheived ->', prediction_accuracy, '%' ))
```

>>>>

```{r}
# imports
library(ggplot2)
library(cowplot)
library(reshape2)
library(factoextra)
```

@@

```{r}
# Calculation of best 'K'
elbow_graph_data <- data.frame(K=integer(), sum_of_square=double())
for(k in seq(1, 10, by=1)){
  km.res <- kmeans(as.matrix(scale(iris_data[,1:4])), k, nstart = 25)
  elbow_graph_data[nrow(elbow_graph_data) + 1, ] = c(k, km.res$tot.withinss)
}
```

@@

```{r}
cm <- table(iris_data$Species, best_km$cluster)
cm
```

```{r}
best_km$centers
```

```{r}
# renaming predicted clusters according to categorical response variable
# renamed_clusters <- c("versicolor", "setosa", "virginica")[best_km$cluster]
```

```{r}
kmeans_basic_table <- data.frame(best_km$size, best_km$centers)
kmeans_basic_table
```

```{r}
kmeans_basic_df <- data.frame(actual_value=iris_data[,5], prediction=best_km$cluster)
kmeans_basic_df
```

@@

```{r}
# prediction_accuracy <- round(sum(kmeans_basic_df$actual_value == kmeans_basic_df$prediction) / nrow(kmeans_basic_df) * 100, 2)
# print(paste('Accuracy Acheived ->', prediction_accuracy, '%' ))
```

### Plotting Clusters

```{r}
fviz_cluster(best_km, data=scale(iris_data[,1:2]), geom=c("point"), ellipse.type = "euclid")
```
***Analysing For K=4***

```{r}
alt_kmeans <- kmeans(as.matrix(scale(iris_data[,1:4])), 4, nstart = 25)
alt_kmeans
```

```{r}
cm <- table(iris_data$Species, alt_kmeans$cluster)
cm
```

```{r}
alt_kmeans$centers
```

```{r}
alt_kmeans_table_size_v_centers <- data.frame(alt_kmeans$size, alt_kmeans$centers)
alt_kmeans_table_size_v_centers
```

```{r}
alt_kmeans_row_pred <- data.frame(actual_value=iris_data[,5], prediction=alt_kmeans$cluster)
alt_kmeans_row_pred
```

```{r}
# clusters = data.frame(alt_kmeans$cluster)
# clusters[clusters$alt_kmeans.cluster==4,]
mapped_data <- data.frame(iris_data[,1:4], prediction=alt_kmeans$cluster)
```

```{r}
# Summary for Cluster 1
summary(mapped_data[mapped_data$prediction==1,1:4])
```

```{r}
# Summary for Cluster 2
summary(mapped_data[mapped_data$prediction==2,1:4])
```

```{r}
# Summary for Cluster 3
summary(mapped_data[mapped_data$prediction==3,1:4])
```

```{r}
# Summary for Cluster 4
summary(mapped_data[mapped_data$prediction==4,1:4])
```

```{r}
fviz_cluster(best_km, data=scale(iris_data[,1:2]), geom=c("point"), ellipse.type = "euclid")
```
